---
title: "p8105_hw5_wl2829"
author: "Wentong"
date: "11/19/2021"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(dplyr)
library(stringr)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

```{r}
homicide_df = 
  read_csv("./data/homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved"
    )
  ) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
```

Focus on Baltimore, MD

```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary = 
  baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

baltimore_test = 
  prop.test(
    x = baltimore_summary %>% pull(unsolved),
    n = baltimore_summary %>% pull(n)
)

baltimore_test %>% 
  broom::tidy()
```

Iterate across cities!

```{r}
prop_test_function = function(city_df){
  city_summary = 
    city_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )

  city_test = 
    prop.test(
      x = city_summary %>% pull(unsolved),
      n = city_summary %>% pull(n)
    )
  return(city_test)
}

homicide_df %>% 
  filter(city_state == "AlbuquerqueNM") %>% 
  prop_test_function()
```

Iterate across all cities.

```{r}
results_df = 
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```

Make a plot showing estimates and confidence intervals.

```{r}
results_df %>% 
  mutate(
    city_state = fct_reorder(city_state, estimate)
  ) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

```{r}
homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  ) %>% 
  mutate(
    test_results = map2(unsolved, n, prop.test),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```

## Problem 2

Create a dataframe including every files
```{r}
file_name_df = 
  tibble(
    files_name = list.files("./data/problem2_data")
  )
```

Iterate over file names and read in data for each subject
```{r, message=FALSE}
file_content = file_name_df %>%
  mutate(file_contents = map(files_name,      
           ~ read_csv(file.path("./data/problem2_data", .))) 
  )
```

Tidy the result
```{r}
file_df = 
  file_content %>% 
  separate(files_name, into = c("arm", "subjectID", sep = "file_type")) %>% 
  select(arm, subjectID, file_contents) %>% 
  unnest(file_contents) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "day",
    values_to = "data"
  ) %>%
  mutate(arm = recode(arm, 'con'='control', 'exp'='experimental'))

file_df 
```

Make a spaghetti plot (experimental vs control)
```{r}
file_df %>% 
  ggplot(aes(x = day, y = data, group = subjectID, color = subjectID)) +
  geom_line() +
  facet_grid(. ~ arm) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  ggtitle("Observations on each subject over time")
```
From the plot, we can compare the data of two groups. The experimental data is higher than the other set of data, and there is a gradual upward trend from week_1 to week_8. Although the data trend of control group is relatively stable, there are still some fluctuations in each group in the middle of the week.

## Problem 3

Load the datasets and fill in the missing values.
```{r}
library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

Use vector function to fill in missing values. 
```{r}
fill_in_missing = function(vector){
  
  if(is.numeric(vector)){
    vector = ifelse(is.na(vector), mean(vector, na.rm = TRUE), vector)

  }
  else{
    vector = ifelse(is.na(vector), "virginica", vector)
  }
}

output = map(iris_with_missing, fill_in_missing)

results_df = bind_rows(output)

results_df

```



